# Project 1
Haoran Zhu

## 1. Code for reading in the dataset and/or processing the data

```{r}
activity<-read.csv("activity.csv")
```

## 2. Histogram of the total number of steps taken each day

```{r}
stepsPerDay<- aggregate(activity$steps,by=list(activity$date),FUN=sum,na.rm = TRUE)
colnames(stepsPerDay)<-c("date","steps")
hist(stepsPerDay$steps)
```

## 3. Mean and median number of steps taken each day

```{r}
stepsPerDayMean<-mean(stepsPerDay$steps)
stepsPerDayMean
stepsPerDayMedian<-median(stepsPerDay$steps)
stepsPerDayMedian
```

## 4. Time series plot of the average number of steps taken

```{r}
stepsPerInterval<-aggregate(activity$steps,by=list(activity$interval), FUN=mean,na.rm = TRUE)
colnames(stepsPerInterval)<-c("interval","steps")
plot(stepsPerInterval$interval,stepsPerInterval$steps,type = "l")
```

## 5. The 5-minute interval that, on average, contains the maximum number of steps

```{r}
MaxstepsPerInterval<-stepsPerInterval[which.max(stepsPerInterval$steps),]$interval
MaxstepsPerInterval
```

## 6. Code to describe and show a strategy for imputing missing data

```{r}
missingValue<-sum(is.na(activity$steps))
missingValue
Mean<-mean(activity$steps,na.rm=TRUE)
Mean
for(i in nrow(activity)){
if(is.na(activity[i,]$steps)==TRUE){activity[i,]$steps<-Mean}
}
```

## 7. Histogram of the total number of steps taken each day after missing values are imputed

```{r}
stepsPerDayWithNA<- aggregate(activity$steps,by=list(activity$date),FUN=sum)
colnames(stepsPerDayWithNA)<-c("date","steps")
hist(stepsPerDayWithNA$steps)
```

## 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
activity$date <- as.Date(activity$date, format="%Y-%m-%d")
activity$day<-weekdays(activity$date)
for (i in 1:nrow(activity)) {
  if (activity[i,]$day=="星期六"|activity[i,]$day=="星期日") {
    activity[i,]$day<-"weekend"
  }
  else  {
    activity[i,]$day<-"weekday"
  }
}
Averagesteps<- aggregate(activity$steps,by=list(activity$day,activity$interval), FUN=mean,na.rm = TRUE)
colnames(Averagesteps)<-c("day","interval","steps")
library(lattice)
xyplot(steps ~ interval | day, Averagesteps, type = "l", layout = c(1, 2), 
       xlab = "Interval", ylab = "Steps")

```
